---
title: 'Example: Files all in same folder as .Rproj'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path = "report2-figs/")
library(tidyverse)
library(NHANES)
```

# Instructions

1. Open the file `report2_clean_data.R` and look at the code. Where is the data located? Where is this .R file that we source located?
2. Knit this file. Where does the output file go?
3. Where do the figures go?
4. Where is the output data?

# NHANES Data

## Data Info

The NHANES data is a subset of the larger [CDC NHANES survey data](https://wwwn.cdc.gov/nchs/nhanes/) found in the R package [`NHANES`](https://cran.r-project.org/web/packages/NHANES/index.html).

```{r data_clean}
# Source an R file in the same folder to load and clean up the data a little bit.
source("report2_clean_data.R")
```

After filtering by age (>=20 years old for valid BMI measurements) and removing subjects with missing BMI, there are `r nrow(nhanes_adult)` study participants.


# Visualizations

Here we use `ggplot2` package to plot BMI by physical activity status, stratified by gender.

```{r physactive_bmi_gender_boxplot}
ggplot(nhanes_adult, aes(x = PhysActive, y = BMI, fill = Gender)) + geom_boxplot()
```

```{r}
# save filtered data
write_csv(nhanes_adult, path="report2-output/nhanes_adult.csv")
```


