---
title: "Report 1"
author: "Your Name Here"
date: "July 18, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/")
```



# This is a section header

## Sub-section header

A shortcut to add a new r chunk is 

- on a Mac: cmd-opt-i
- on a PC: ctrl-alt-i

# To Do

1. Try compiling this document using the "Knit" button. What files are produced?
2. Edit the output to be "pdf_document" and recompile. What files are produced?
3. Edit the output to be "word_document" and recompile. What files are produced?

4. Explore this code chunk:

```{r}
x = rnorm(100)
hist(x)
```

5. We can add a name to our chunk. What does this do?

```{r histonorm}
x = rnorm(100)
hist(x)
```

6. Look at the chunk options below. Chunk options go after the chunk name and a comma. What does changing fig.height= something else do?

```{r smallfig, fig.height=2}
x = rnorm(100)
hist(x)
```

7. Add the chunk option echo=FALSE to the chunk below and see what happens. Note that the global option was set in the first setup chunk to have echo=TRUE.

```{r}
x = rnorm(100)
hist(x)
```

8. Uncomment this code and recompile the document. Then add a chunk command cache=TRUE and recompile. What files are created? Try compiling one more time. 

```{r longtime}
#Sys.sleep(10)
```

9. Add your own code chunk and print the length of `x`.
