---
title: 'Example: Files in subfolder from main .Rproj folder - with here()'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path = here::here("figs","report3-here/"))
library(tidyverse)
library(NHANES)
```

# Instructions

1. Open the file `report3-here/report3_clean_data.R` and look at the code. Where is the data located? Where is this .R file that we source located?
2. Knit this file. Where does the output file go?
4. Where is the output data?
5. Open the file `report3-here/report3_clean_data.R` and run the code. What happens and why?
6. In the console, type the code below (or run interactively from this .Rmd file). What is the output?

```{r, eval=FALSE}
here::here()

here::here("data", "myfile.csv")
```


# NHANES Data

## Data Info

The NHANES data is a subset of the larger [CDC NHANES survey data](https://wwwn.cdc.gov/nchs/nhanes/) found in the R package [`NHANES`](https://cran.r-project.org/web/packages/NHANES/index.html).

```{r data_clean}
# Source an R file in the same folder to load and clean up the data a little bit.
source("report3_clean_data.R")
# this also works:
# source(here::here("report3-here","report3_clean_data.R"))
```

After filtering by age (< 18 years old) and removing subjects with missing BMI, there are `r nrow(nhanes_kids)` children study participants.


# Visualizations

Here we use `ggplot2` package to plot BMI by physical activity status, stratified by gender.

```{r physactive_bmi_gender_boxplot}
ggplot(nhanes_kids, aes(x = PhysActive, y = BMI, fill = Gender)) + geom_boxplot()
```

```{r}
# save filtered data
# create output folder first
fs::dir_create(here::here("output"))
# save as csv file
write_csv(nhanes_kids, path=here::here("output","nhanes_kids_here.csv"))
```


