---
title: 'Example: Report2 as a presentation'
author: 'Your name here'
date: "`r Sys.Date()`"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE)
library(tidyverse)
library(xaringan)
```

# Instructions

1. Knit the document.
2. Change the output type to ioslides_presentation and knit. How are the new slides created?
3. Change the output type to slidy_presentation and knit.
4. Change the output type to xaringan::moon_reader and knit. What happened to the slides?
5. Try changing the output type to powerpoint_presentation. If you have powerpoint installed this should work ok.

# NHANES Data

## Data Info

The NHANES data is a subset of the larger [CDC NHANES survey data](https://wwwn.cdc.gov/nchs/nhanes/) found in the R package [`NHANES`](https://cran.r-project.org/web/packages/NHANES/index.html).

```{r data_clean}
# load the data
nhanes_data <- read_csv("example4_nhanes_data.csv")

# filter data to study only adults with BMI values
nhanes_adult <- nhanes_data %>% drop_na(BMI) %>% filter(Age >= 20)
```

After filtering by age (>=20 years old for valid BMI measurements) and removing subjects with missing BMI, there are `r nrow(nhanes_adult)` study participants.


# Visualizations

Here we use `ggplot2` package to plot BMI by physical activity status, stratified by gender.

```{r physactive_bmi_gender_boxplot}
ggplot(nhanes_adult, aes(x = PhysActive, y = BMI, fill = Gender)) + geom_boxplot()
```



