---
title: 'Example: Files all in same folder'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path = "figs/")
library(tidyverse)
```

# Instructions

1. Look at the chunk labeled data_clean below. Where is the data located in relation to this .Rmd file and to your project folder?
2. Knit this file. The file creates an output file with filtered data. Where does the output file go?
3. Where do the figures go?
5. Change the code in `data_clean` chunk to read in the data from `berd_rmarkdown_project/data/nhanes_data_females.csv`.
6. Change the code in `save_data` chunk to save the output file in `berd_rmarkdown_project/output/`.

# NHANES Data

## Data Info

The NHANES data is a subset of the larger [CDC NHANES survey data](https://wwwn.cdc.gov/nchs/nhanes/) found in the R package [`NHANES`](https://cran.r-project.org/web/packages/NHANES/index.html).

```{r data_clean}
# load the data
nhanes_data <- read_csv("example4_nhanes_data.csv")

# filter data to study only adults with BMI values
nhanes_adult <- nhanes_data %>% drop_na(BMI) %>% filter(Age >= 20)
```

After filtering by age (>=20 years old for valid BMI measurements) and removing subjects with missing BMI, there are `r nrow(nhanes_adult)` study participants.

# Visualizations

Here we use `ggplot2` package to plot BMI by physical activity status, stratified by gender.

```{r physactive_bmi_gender_boxplot}
ggplot(nhanes_adult, aes(x = PhysActive, y = BMI, fill = Gender)) + geom_boxplot()
```

# Save the output

```{r save_data}
# save filtered data
write_csv(nhanes_adult, path="output/nhanes_adult.csv")
```


# Here

What is the here::here() location?

```{r}
here::here()
```

